### 2025-05-16 chapters/introduction/intro.Rnw
Minor edit to help distinguish SSM from mechanistic

The importance of time series analysis has continued to grow with the demand for both the collection and analysis of data.
Time series data are abundant, as data are often generated over time in a way that introduces dependence between observations. 
However, the analysis of time series presents a unique challenge for both statisticians and practitioners, as the temporal dependence between observations requires careful treatment.
A unifying approach in time series analysis, known as state space modeling, assumes that observations from the system under investigation depend on an unobservable process.
Constructing a state space model involves proposing equations that describe the evolution of this unobservable process over time and the unobserved process is related to observations.
Common goals of state space modeling include making inferences about critical yet unobserved variables, incorporating real-world mechanisms into statistical models, and enabling likelihood based inference for models who that lack closed-form expressions of the likelihood function.

>>>>

The importance of time series analysis has continued to grow with the demand for both the collection and analysis of data.
Time series data are abundant, as data are often generated over time in a way that introduces dependence between observations. 
However, the analysis of time series presents a unique challenge for both statisticians and practitioners, as the temporal dependence between observations requires careful treatment.
A unifying approach in time series analysis, known as state space modeling, assumes that observations from the system under investigation depend on an unobservable process.
Constructing a state space model involves proposing equations that describe the evolution of this unobservable process over time and the unobserved process is related to observations.
Common goals of state space modeling include making inferences about critical yet unobserved variables, incorporating real-world mechanisms into statistical models, or enabling likelihood based inference for models that lack closed-form expressions of the likelihood function.
